\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-31 popl-2019-journal-v/proving-full-abstraction.tex
[POPLjv] Add untrusted value relation mono lemma

\lau{TODO: insert monotonicity lemma}
\paragraph{The trusted value relation}
\label{par:trusted-val-rel}
The trusted value relation $\lrvname_\trusted$ relates everything safe for a trusted component to have without breaking memory invariants.
For the most part, we allow them to contain the same words as the untrusted components, but we also need to allow them to have seal sets with trusted closure seals and return seals which we cannot allow untrusted components to have.
Further, we need to allow trusted components to have capabilities for the trusted code which, again, is something that we cannot allow untrusted components to have.
The untrusted value relation is defined in Figure~\ref{fig:trusted-val-rel}.

>>>>

Words given to untrusted code may be stored by the untrusted code for later use.
This means that a word is only safe to give to untrusted code if it is safe for them to keep it.
This means that the untrusted value relation must be monotone with respect to the world, so words stay safe in any possible future world.
\begin{lemma}[Untrusted value relation monotonicity]
  \label{lem:monotonicity}
  For all integers $n$, words $w_1$ and $w_2$, and worlds $W' \future W$, if $\npair{(w_1,w_2)} \in \lrv(W)$, then $\npair{(w_1,w_2)} \in \lrv(W')$.
\end{lemma}

\paragraph{The trusted value relation}
\label{par:trusted-val-rel}
The trusted value relation $\lrvname_\trusted$ relates everything safe for a trusted component to have without breaking memory invariants.
For the most part, we allow them to contain the same words as the untrusted components, but we also need to allow them to have seal sets with trusted closure seals and return seals which we cannot allow untrusted components to have.
Further, we need to allow trusted components to have capabilities for the trusted code which, again, is something that we cannot allow untrusted components to have.
The untrusted value relation is defined in Figure~\ref{fig:trusted-val-rel}.
